\documentclass{article}
\usepackage[utf8]{inputenc}
\begin{document}
Alex is a senior majoring in EECS at UC Berkeley. He loves \textbf{\textit{Hiking}} and traveling alone. Once two weeks Alex will go to Yosemite by himself to go hike those real crazy hard trails because he is really confident about his hiking skills. Alex is too arrogant that he never brings his bear spray even though he knows it’s highly possible to encounter a bear when doing solo hike. He just hates hiking with people that he thinks that everyone’s pace is slower than his and he has to take care of everyone which he thinks it's a waste of time. \\
\newline
	\indent As usual Alex wakes up at 6 in the morning and is ready to do his favorite activity -- \textbf{Solo Hike}. He drives all the way to Yosemite, getting the park permission and are all set to challenge the most difficult hiking trail in Yosemite -- \textbf{The Bear Claw}. The Bear Claw trail is known to be extremely difficult for solo hikers. The grizzly Bear’s footprints, the scratches on the tree made by bear’s claw are all over the pathway. However, Alex is not afraid of anything; he claims that he can kill a grizzly bear without using any tools, As Alex starts hiking, he hears bear’s roars and and sees bear all over the mountain. But he’s still not afraid of them. Halfway through his walk, he sees a huge, bulky grizzly bear staring at him, hissing and giving warnings to the unwelcome stranger not to get closer to its territory, However, the arrogant Cal student refuses to obey the signal and decides to challenge the bear. As Alex keeps walking towards the brutal creature, the bear launches a surprise attack, giving Alex a huge scratch right across his chest. The aggressive grizzly bear knocks Alex down and and soon it leaves the place. When Alex wakes up the following day, he realizes that there is something wrong with his body. He found out that he can, in fact, transforms into a bear whenever he likes.

Path Alex doing nothing
Once back in Berkeley, Alex began to shy away from the responsibility that his new bear powers had given him. As an EECS major, Alex always knew he would be a \textit {god amongst \emph {men}, a king amongst \emph {peasants} and a genius amongst \emph {plebeians} but he was afraid} of the responsibilities. He feared having to use the powers for reasons other than \textbf {beating up bullies that made fun of him, attacking professors for giving him ninety-nine instead of one hundred on exams and eating other EECS students that were in competition for internships} would impose too large a burden for him to handle. The possibility of using his bear powers for good was \textbf {out of the question.} Alex suppressed his urge to go \textit {full bear} and instead decided to dedicate his life to his studies so he could graduate and rule the world one technology company at a time. 










Path Alex fights crime
The next day, Alex decides to begin his journey of crime fighting. He buys an old police radio from a local pawn shop and listens to it in the background as he completes is CS lab. Around 11 pm, he hears something of interest! \textit{Calling all available units, robbery in progress at the Bank of America on Telegraph and Durant.} “Perfect!” Alex exclaims. The bank was right down the street and he could be there in minutes! He runs out of his apartment and begins his transformation as he heads toward the bank. When he arrives, he promptly breaks down the bank’s door with his increased strength, frightening the two robbers and the bank teller. He unleashes an ear-shattering roar, scaring the robbers so much that they drop their loot and begin looking for a way to escape. As the robbers scramble to make a new plan, Alex charges and swings at them with his sharp talons. Due to the shear force with which they were attacked, the robbers died quickly before truly understanding what had happened. Alex spends a short moment admiring his gruesome work before leaving the bloody scene. As he exits he shifts back to his normal form, getting a safe distance from the crime scene just before the police show up. 





Main path
Passing through Sproul plaza in the afternoon, Alex saw a group of protesters advocating people to kill bears. They claimed that bear is a dangerous animal that we might risk our lives if we encounter bears in the wild, or even in the bear territory -- our main campus.
  





Path engage in protest
Given his new connection to the bear community, Alex is outraged by the protesters. He decides he wants to teach them a lesson about the \textbf{mighty power of bears!} Alex walks to the other side of Sproul hall where he can remain out of sight, and transforms into a formidable Grizzly. Once in full form, he runs back to the protest and unleashes a horrifying roar! Chaos ensues as people run in all directions in hope of safety. However, the protest’s leader stands his ground. As he stands on the steps of upper Sproul, he turns to Alex and directs his hate speech toward him. Furious at the arrogance of this bigot, Alex charges him. Although the police were on site, they did not have time to stop Alex before he sunk his claws and teeth into the protester’s shoulder and torso. The protester unleashed horrible screams as he was whipped back and forth by the bear’s superior strength. Alex releases the dead man and tries to flee toward Strawberry Creek. But now that the police have had time to organize, they are prepared. Unsurprisingly, the officers did not expect any kind of bear attack and thus did not carry with them any appropriate tranquilizers. They were left with only one option… \textbf{/emp{shoot the bear dead.}} So, just as Alex was approaching Sather Gate, one brave officer aimed, and shot the bear dead with one bullet. In the end, instead of helping fight the hateful messages being said about bears, Alex died only to strengthen their cause. 







Path ignore protest
Alex took one glance at the protestors and walked away. Even though the protestors advocated for the killing of bears around the world because of the health benefits within bear meat, Alex felt that getting a good night’s rest for his final the next day was far more important. While Alex could have taken action and fought for bear rights by turning into a bear and mauling the protestors with his giant paws, he was uninterested. Assuming \textit {bear form} detracted from Alex’s true goal of ruling the world with his superior intellect. Uninterested in the protest, Alex continued walked home. He heard the faint shouts of “Bear meat is fair meat” through his headphones, but did not even turn around.






Path Alex Dies
As Alex approached his apartment, he took out his keys to open the door. Suddenly, he heard footsteps behind him. Alex turned around and saw a man holding a signed that read \textit {“More Bears More Problems.”} Stunned, Alex inquired if the guy needed something. The man pointed to Alex’s laptop yelling “That bear sticker of yours makes you look like a bear supporter boy.” The man pulled out a sword from his pocket and struck down Alex with one swing. Alex’s body split in half and landed on the floor with a loud \textbf {thud.} Alex’s belongings dropped to the floor, drowning in a pool of his blood.

\end{document}
