\documentclass{article}
\usepackage[utf8]{inputenc}
\begin{document}
Alex is a senior majoring in EECS at UC Berkeley. He loves \textbf{\textit{Hiking}} and traveling alone. Once two weeks Alex will go to Yosemite by himself to go hike those real crazy hard trails because he is really confident about his hiking skills. Alex is too arrogant that he never brings his bear spray even though he knows it’s highly possible to encounter a bear when doing solo hike. He just hates hiking with people cuz he thinks that everyone’s pace is slower than his and he has to take care of everyone which he thinks it's a waste of time. \\

	As usual Alex wakes up at 6 in the morning and is ready to do his favorite activity -- \textbf{Solo Hike}. He drives all the way to Yosemite, getting the park permission and are all set to challenge the most difficult hiking trail in Yosemite -- \textbf{The Bear Claw}. The Bear Claw trail is known to be extremely difficult for solo hikers. The grizzly Bear’s footprints, the scratches on the tree made by bear’s claw are all over the pathway. However, Alex is not afraid of anything; he claims that he can kill a grizzly bear without using any tools, As Alex starts hiking, he hears bear’s roars and and sees bear all over the mountain. But he’s still not afraid of them. Halfway through his walk, he sees a huge, bulky grizzly bear staring at him, hissing and giving warnings to the unwelcome stranger not to get closer to its territory, However, the arrogant Cal student refuses to obey the signal and decides to challenge the bear. As Alex keeps walking towards the brutal creature, the bear launches a surprise attack, giving Alex a huge scratch right across his chest. The aggressive grizzly bear knocks Alex down and and soon it leaves the place. When Alex wakes up the following day, he realizes that there is something wrong with his body. Hu found out that he can, in fact, transforms into a bear whenever he likes.

\end{document}